Incentivizing Exploration with Unbiased History

### 2018-10-27 2level.tex
finished edits

%!TEX root = main.tex
\section{Warm-up:  2-Level Explore-then-Exploit Policy}
\swedit{Now we provide a simple policy that can incentivize the agents
  to perform non-adaptive exploration and achieve a regret rate of
  $\tilde O(T^{2/3})$. The policy essentially follows the
  ``explore-then-exploit'' paradigm and consists two phases, which can
  be described as a two-level information graph (as shown in
  Figure~\ref{fig:2level}).  In the first level, we perform
  exploration by simulating $T_1$ independent runs \ALGG of $\GdT$
  rounds. This is done by randomly dividing the first $T_1 \cdot \GdT$
  agents into $T_1$ groups of equal size and each agent only observe
  the history of all previous agents in the same group.  In the second
  level, we ``exploit'' by showing all the remaining agents the entire
  history of first phase.

  The key idea behind the policy is that the first level effectively
  boosts the exploration probability of Greedy. Since each run of
  \ALGG explores all arms with constant probability (Lemma
  \ref{lem:greedy}), by simulating multiple runs of Greedy, we can
  ensure that with high probability, every arm is pulled with a
  sufficient number of times. The following Lemma follows from
  applying Chernoff bound and union bound.

}

\begin{lemma}[Concentration of arm pulls]\label{lem:t1runs}
  Consider $T_1$ indepdent runs of \ALGG of length $T_G$. Let $N_a$ be
  the number of arm $a$ pulls among all runs. Then with probability at
  least $1-\delta$, for all $a\in \A$,
  \[
    \left| N_a - q_a T_1\right| \leq T_G \sqrt{T_1 \log(2K/\delta) / 2}
  \]
\end{lemma}

@@

\swedit{As a result, every agent in the second level will pull an arm
  with mean rewards close to the optimal, which gives us the following
  regret guarantee.}

@@

\swcomment{I think this proof should go to appendix, so I didn't do
  too much refactoring}

@@

  The first $T_1 \cdot \GdT$ rounds will get total regret at most
  $T_1 \cdot \GdT$.  We focus on bounding the regret from the second
  level of $T - T_1 \cdot \GdT$ rounds. We consider the following two
  clean events. We will first bound the probability that both of them
  happen and then we will show that they together imply upper bounds
  on $|\hat{\mu}^t_a - \mu_a|$'s for any agent $t$ in the second
  level. Recall $\hat{\mu}^t_a$ is the estimated mean of arm $a$ by
  agent $t$ and agent $t$ picks the arm with the highest
  $\hat{\mu}^t_a$.

@@

\begin{remark}
  If the gap parameter $\Delta$ is known to the principal, we can set
  $$T_1 = \max\left( \frac{4\GdT^2}{\GdP^2}\log(T), \frac{36 }{\Delta^2
      \cdot p_G} \log(T) \right)$$, and achieves an expected regret of
  $O(\log(T) \cdot \Delta^{-2})$.
\end{remark}

>>>>

%!TEX root = main.tex
\section{Warm-up:  2-Level Explore-then-Exploit Policy}
\swedit{Now we provide a simple policy that can incentivize the agents
  to perform non-adaptive exploration and achieve a regret rate of
  $\tilde O(T^{2/3})$. The policy essentially follows the
  ``explore-then-exploit'' paradigm and consists of two phases, which can
  be described as a two-level information graph (as shown in
  Figure~\ref{fig:2level}).  In the first level, we perform
  exploration by simulating $T_1$ independent runs of \ALGG of $\GdT$
  rounds. This is done by randomly dividing the first $T_1 \cdot \GdT$
  agents into $T_1$ groups of equal size and allowing each agent to only observe
  the history of all previous agents in the same group.  In the second
  level, we ``exploit'' by showing all the remaining agents the entire
  history of first phase.

  The key idea behind the policy is that the first level effectively
  boosts the exploration probability of \ALGG. Since each run of
  \ALGG explores all arms with constant probability (Lemma
  \ref{lem:greedy}), by simulating multiple runs of \ALGG, we can
  ensure that with high probability, every arm is pulled a
  sufficient number of times. The below lemma follows from
  concentration bounds.

} \nicomment{there was a proof of this once; i remember checking it. if it still exists, let's throw it in an appendix.}

\begin{lemma}[Concentration of arm pulls]\label{lem:t1runs}
  Consider $T_1$ indepdent runs of \ALGG of $T_G$ rounds. Let $N_a$ be
  the number of arm $a$ pulls among all runs. Then with probability at
  least $1-\delta$, for all $a\in \A$,
  \[
    \left| N_a - q_a T_1\right| \leq T_G \sqrt{T_1 \log(2K/\delta) / 2}
  \]
\end{lemma}

@@

\swedit{As a result, every agent in the second level will pull an arm
  with mean reward close to the optimal, which gives us the following
  regret guarantee.}

@@

\swcomment{I think this proof should go to appendix, so I didn't do
  too much refactoring} \nicomment{I read this last week and talked to jieming about it; seemed right but a bit messy, but since it's going in an appendix i won't re-read/edit it now.}

@@

  The first $T_1 \cdot \GdT$ rounds will get total regret at most
  $T_1 \cdot \GdT$.  We focus on bounding the regret from the second
  level of $T - T_1 \cdot \GdT$ rounds. We consider the following two
   events. We will first bound the probability that both of them
  happen and then we will show that they together imply upper bounds
  on $|\hat{\mu}^t_a - \mu_a|$'s for any agent $t$ in the second
  level. Recall $\hat{\mu}^t_a$ is the estimated mean of arm $a$ by
  agent $t$ and agent $t$ picks the arm with the highest
  $\hat{\mu}^t_a$.

@@

\begin{remark}
  If the gap parameter $\Delta$ is known to the principal, we can set
  $$T_1 = \max\left( \frac{4\GdT^2}{\GdP^2}\log(T), \frac{36 }{\Delta^2
      \cdot p_G} \log(T) \right),$$ and achieve an expected regret of
  $O(\log(T) \cdot \Delta^{-2})$.
\end{remark}

### 2018-10-27 model.tex
finished edits

% We mostly focus on the case when $K=2$. We also discuss how to
% generalize our results to the case when $K$ is a constant greater
% than 2. The messages $m_t$ are generated according to a randomized
% online algorithm $\pi$ termed ``recommendation policy".

\xhdr{Unbiased sub-history policy.} The principal's goal is to reveal
a sequence of messages accroding to a disclosure policy so that the
regret of the induced sequence of actions is minimized. We will focus
on \emph{unbiased sub-history policies} that at each round $t$ reveal
the \emph{sub-history} $H_t = \{(s, a_s, r_s)\mid s \in S_t\}$, such
that each $S_t\subseteq [t-1]$ is a subset of previous rounds
\emph{fixed ahead of time}. A simple example is the policy that
reveals the \emph{full history} with $S_t = [t-1]$.  All of the
policies we develop are \emph{transitive}: for any two agents $t$ and
$t'$ such that $t'\in S_t$, then the sub-history of $S_t$ contains
that of $S_{t'}$.

\xhdr{Information flow graph.} We will describe our transitive
policies using a \emph{information flow graph} (and henceforth
\emph{information graph})---a directed graph over the $T$ agents such that if
there is an edge from $u$ to $v$, it means $u\in S_v$. By the property
of transitivity, $S_t$ is the set of nodes that can reach node $t$ in
the info graph.

@@

\xhdr{Agents' behavior.} We model agents with heterogeneity in their arm selections. In particular, each agent $t$ has a private estimator that maps the revealed sub-history $H_t$ to a mean reward estimate $\hat{\mu}_a^t$ for every arm $a$, and the agent chooses the arm $a_t$ with the highest estimate. The agents' private estimators are drawn i.i.d.~from an unknown distribution. For any $t\in[T]$ and $a\in \A$, we write $N_{t, a}$ and $\bar{\mu}_a^t$ to denote the number of pulls of $a$ and the empirical mean reward of arm $a$ in sub-history $H_t$ respectively. If an arm is not pulled in $H_t$, we will let $\bar{\mu}_a^t = 0$.  We require the following assumptions.

% \swcomment{need to assume i.i.d. types}
% We assume that for sufficiently high $t_a$, the estimate
% $\hat{\mu}_a^t$ is close to the empirical average $\bar{\mu}_a^t$.

@@

We allow different agents to have different behavior models as long as
they satisfy Assumption \ref{ass:embehave}. More specifically, we
assume each agent's behavior model is sampled from an unknown
distribution independently.
% \swcomment{why independently? can be be
%   adversarial?} \jmcomment{Actually current proofs don't work when it's adversarial. It's fairly annoying for the anti-concentration argument. In the proof, we need to use independent to show that the amount of agents pulling arm $a$ in the first level is concentrated to $T_1 q_a$.}
\begin{remark}
  how this relates to Bayesian exploration with conjugate
  priors\swcomment{seems to be something nasty} \nicomment{need to at least say if we rule out rational agents with these assumptions (which I don't think is a disaster).}
\end{remark}

>>>>

\xhdr{Unbiased sub-history policy.} The principal's goal is to reveal a sequence of messages according to a disclosure policy so that the regret of the induced sequence of actions is minimized. We will focus on \emph{unbiased sub-history policies} that at each round $t$ reveal the \emph{sub-history} $H_t = \{(s, a_s, r_s)\mid s \in S_t\}$, such that each $S_t\subseteq [t-1]$ is a subset of previous rounds \emph{fixed ahead of time}. A simple example is the policy that reveals the \emph{full history} with $S_t = [t-1]$.  All of the policies we develop are \emph{transitive}: for any two agents $t$ and $t'$ such that $t'\in S_t$, then the sub-history of $S_t$ contains that of $S_{t'}$.

\xhdr{Information flow graph.} We will describe our transitive policies using a \emph{information flow graph} (and henceforth \emph{information graph})---a directed graph over the $T$ agents such that if there is an edge from $u$ to $v$, it means $u\in S_v$. By the property of transitivity, $S_t$ is the set of nodes that can reach node $t$ in the info graph. \niedit{For example, an information graph for the policy that reveals the full history is the directed line graph containing edges $(t,t+1)$ for all $t\in[T-1]$.}

@@

\xhdr{Agents' behavior.} \nicomment{re-ordered this.} An {\em agent estimator} is a function that maps the revealed sub-history $H_t$ to a mean reward estimate $\hat{\mu}_a^t$ for every arm $a$. For any $t\in[T]$ and $a\in \A$, we write $N_{t, a}$ and $\bar{\mu}_a^t$ to denote the number of pulls of $a$ and the empirical mean reward of arm $a$ in sub-history $H_t$ respectively. If an arm is not pulled in $H_t$, we will let $\bar{\mu}_a^t = 0$.  We require the following assumptions.

@@

We model agents with heterogeneity in their arm selections. In particular, there is an unknown distribution over the set of agent estimators satisfying Assumption~\ref{ass:embehave}.  Each agent $t$ indepedently draws an estimator from this distribution, uses it to calculate the mean reward estimates $\hat{\mu}_a^t$ for every arm $a$, and then chooses the arm $a_t$ with the highest estimate. 
% \swcomment{why independently? can be be
%   adversarial?} \jmcomment{Actually current proofs don't work when it's adversarial. It's fairly annoying for the anti-concentration argument. In the proof, we need to use independent to show that the amount of agents pulling arm $a$ in the first level is concentrated to $T_1 q_a$.}

\begin{remark}
We emphasize that the agents we consider in this paper are {\em frequentists}.  Thus their estimators, which determine their behavior, take samples as inputs and not priors.  The estimators satisfying Assumption~\ref{ass:embehave} include that of the natural greedy frequentist, who always pulls the arm with the highest empirical mean.
\end{remark}
